Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-02-12 submission/appendix.tex
appendix on two pages, more to do

We also remove the following outliers, as identified by visual inspection: \texttt{efficient\_b0,\_b2}.
And we remove the entire \texttt{cifar100} \texttt{ResNeXT} series, which is the only example show no trends with the norm metrics.

The final datasets used are shown in Table~\ref{table:datasets}.
The final architecture series used are shown in  Table~\ref{table:architectures}, with the number of models in each.

@@

\begin{figure}[t]
    \centering
    \subfigure[ImageNet 1K]{
        \includegraphics[width=2.5cm]{img/imagenet1k_alpha.png}
        \label{fig:imagenet1k-alpha}
    }
    \qquad
    \subfigure[ CIFAR 10 ]{
        \includegraphics[width=2.5cm]{img/cifar10_alpha.png}
        \label{fig:cifar10.alpha}
    }
    \qquad
    \subfigure[ CIFAR 100 ]{
        \includegraphics[width=2.5cm]{img/cifar100_alpha.png}
        \label{fig:cifar100.alpha}
    }
    \qquad
    \subfigure[ SVHN ]{
        \includegraphics[width=2.5cm]{img/svhn_alpha.png}
        \label{fig:svhn.alpha}
    }
    \qquad
    \subfigure[ CUB 200 ]{
        \includegraphics[width=2.5cm]{img/cub200_alpha.png}
        \label{fig:cub200.alpha}
    }
    \caption{\charles{Preliminary charts:} PL exponent $\alpha$ vs. reported Top1 Test Accuracies for pretrained DNNs available\charles{ref} for 5 different data sets.}
    \label{fig:DSalphas}
\end{figure}

@@

\begin{table}[t]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\log\Vert\cdot\Vert_{F}$ & $\log\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\log\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
\hline
 imagenet-1k & ResNet  & 5.96 &  11.03 & \textbf{3.51} & 4.01 \\
 imagenet-1k & EfficientNet  & 2.67 &  \textbf{1.23} & 2.56 & 2.50 \\
 imagenet-1k & PreResNet  & 6.59 &  15.44 & \textbf{3.59} & 3.71 \\
 imagenet-1k & ShuffleNet  & 35.38 &  89.58 & 19.54 & \textbf{18.48} \\
 imagenet-1k & VGG  & 0.84 &  \textbf{0.68} & 1.89 & 1.59 \\
 imagenet-1k & DLA  & 22.41 &  \textbf{8.49} & 14.69 & 15.68 \\
 imagenet-1k & HRNet  & 0.47 &  0.51 & \textbf{0.16} & 0.16 \\
 imagenet-1k & DRN-C  & 0.60 &  0.66 & \textbf{0.40} & 0.48 \\
 imagenet-1k & SqueezeNext  & 21.94 &  21.39 & 13.31 & \textbf{13.23} \\
 imagenet-1k & ESPNetv2  & 13.77 &  14.74 & \textbf{1.87} & 2.53 \\
 imagenet-1k & IGCV3  & 1.94 &  87.76 & 8.48 & \textbf{1.09} \\
 imagenet-1k & ProxylessNAS  & \textbf{0.19} &  0.26 & 0.28 & 0.26 \\
 imagenet-1k & SqueezeNet  & 0.11 &  0.11 & \textbf{0.07} & 0.08 \\
\hline
 cifar-10 & ResNet  & 0.31 &  0.30 & \textbf{0.28} & 0.28 \\
 cifar-10 & DIA-ResNet  & \textbf{0.05} &  0.08 & 0.28 & 0.32 \\
 cifar-10 & SENet  & 0.09 &  0.09 & \textbf{0.04} & 0.04 \\
\hline
 cifar-100 & ResNet  & 4.13 &  4.50 & \textbf{3.06} & 3.06 \\
 cifar-100 & DIA-ResNet  & \textbf{0.36} &  1.38 & 0.93 & 1.02 \\
 cifar-100 & SENet  & 0.36 &  0.43 & \textbf{0.26} & 0.26 \\
 cifar-100 & WRN  & 0.14 &  0.20 & 0.07 & \textbf{0.06} \\
\hline
 svhn & ResNet  & 0.04 &  0.04 & \textbf{0.02} & 0.02 \\
 svhn & DIA-ResNet  & 0.00 &  \textbf{0.00} & 0.02 & 0.02 \\
 svhn & SENet  & \textbf{0.00} &  0.00 & 0.00 & 0.00 \\
 svhn & WRN  & 0.01 &  0.01 & 0.01 & \textbf{0.01} \\
 svhn & ResNeXt  & 0.00 &  \textbf{0.00} & 0.01 & 0.01 \\
\hline
 cub-200-2011 & ResNet  & 0.20 &  \textbf{0.18} & 3.19 & 3.21 \\
 cub-200-2011 & SENet  & \textbf{1.07} &  1.29 & 1.85 & 1.95 \\
\hline
\end{tabular}
\end{center}
\caption{MSE Results for all CV model regressions. }
\label{table:MSEresults}
\end{table}

\begin{table}[t]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\log\Vert\cdot\Vert_{F}$ & $\log\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\log\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
\hline
imagenet-1k & ResNet  & 0.82 &  0.67 & \textbf{0.90} & 0.88 \\
 imagenet-1k & EfficientNet  & 0.65 &  \textbf{0.84} & 0.67 & 0.67 \\
 imagenet-1k & PreResNet  & 0.73 &  0.36 & \textbf{0.85} & 0.85 \\
 imagenet-1k & ShuffleNet  & 0.63 &  0.06 & 0.80 & \textbf{0.81} \\
 imagenet-1k & VGG  & 0.71 &  \textbf{0.76} & 0.35 & 0.45 \\
 imagenet-1k & DLA  & 0.13 &  \textbf{0.67} & 0.43 & 0.39 \\
 imagenet-1k & HRNet  & 0.91 &  0.90 & \textbf{0.97} & 0.97 \\
 imagenet-1k & DRN-C  & 0.81 &  0.79 & \textbf{0.87} & 0.85 \\
 imagenet-1k & SqueezeNext  & 0.05 &  0.07 & 0.42 & \textbf{0.43} \\
 imagenet-1k & ESPNetv2  & 0.42 &  0.38 & \textbf{0.92} & 0.89 \\
 imagenet-1k & IGCV3  & 0.98 &  0.12 & 0.92 & \textbf{0.99} \\
 imagenet-1k & SqueezeNet  & 0.01 &  0.00 & \textbf{0.38} & 0.26 \\
 imagenet-1k & ProxylessNAS  & \textbf{0.68} &  0.56 & 0.53 & 0.58 \\
\hline
 cifar-10 & ResNet  & 0.58 &  0.59 & \textbf{0.62} & 0.61 \\
 cifar-10 & DIA-ResNet  & \textbf{0.96} &  0.93 & 0.74 & 0.71 \\
 cifar-10 & SENet  & 0.91 &  0.91 & \textbf{0.96} & 0.96 \\
\hline
 cifar-100 & ResNet  & 0.61 &  0.58 & \textbf{0.71} & 0.71 \\
 cifar-100 & DIA-ResNet  & \textbf{0.96} &  0.85 & 0.90 & 0.89 \\
 cifar-100 & SENet  & 0.97 &  0.96 & \textbf{0.98} & 0.98 \\
 cifar-100 & WRN  & 0.32 &  0.04 & 0.66 & \textbf{0.69} \\
\hline
 svhn & ResNet  & 0.69 &  0.70 & \textbf{0.82} & 0.81 \\
 svhn & DIA-ResNet  & 0.94 &  \textbf{0.95} & 0.78 & 0.77 \\
 svhn & SENet  & \textbf{0.99} &  0.96 & 0.98 & 0.98 \\
 svhn & WRN  & 0.13 &  0.10 & 0.20 & \textbf{0.21} \\
 svhn & ResNeXt  & 0.87 &  \textbf{0.90} & 0.64 & 0.75 \\
\hline
 cub-200-2011 & ResNet  & 0.94 &  \textbf{0.95} & 0.08 & 0.08 \\
 cub-200-2011 & SENet  & \textbf{0.66} &  0.59 & 0.41 & 0.38 \\
\hline
\end{tabular}
\end{center}
\caption{$R^{2}$ Results for all CV model regressions. }
\label{table:R2results}
\end{table}

>>>>

We remove the following outliers, as identified by visual inspection: \texttt{efficient\_b0,\_b2}.
We also remove the entire \texttt{cifar100} \texttt{ResNeXT} series, which is the only example show no trends with the norm metrics.
%
The final datasets used are shown in Table~\ref{table:datasets}.
The final architecture series used are shown in  Table~\ref{table:architectures}, with the number of models in each.

@@

\begin{figure}[t]
    \centering
    \subfigure[ImageNet 1K]{
        \includegraphics[width=2.5cm]{img/imagenet1k_alpha.png}
        \label{fig:imagenet1k-alpha}
    }
    %\qquad
    \subfigure[ CIFAR 10 ]{
        \includegraphics[width=2.5cm]{img/cifar10_alpha.png}
        \label{fig:cifar10.alpha}
    }
    %\qquad
    \subfigure[ CIFAR 100 ]{
        \includegraphics[width=2.5cm]{img/cifar100_alpha.png}
        \label{fig:cifar100.alpha}
    }
    %\qquad
    \subfigure[ SVHN ]{
        \includegraphics[width=2.5cm]{img/svhn_alpha.png}
        \label{fig:svhn.alpha}
    }
    %\qquad
    \subfigure[ CUB 200 ]{
        \includegraphics[width=2.5cm]{img/cub200_alpha.png}
        \label{fig:cub200.alpha}
    }
    \caption{% 
             %\charles{Preliminary charts:} 
             PL exponent $\alpha$ vs. reported Top1 Test Accuracies for pretrained DNNs available for five different data sets.
            }
    \label{fig:DSalphas}
\end{figure}

@@

\begin{table}[t]
\footnotesize  % \small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\log\Vert\cdot\Vert_{F}$ & $\log\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\log\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
\hline
 imagenet-1k & ResNet  & 5.96 &  11.03 & \textbf{3.51} & 4.01 \\
 imagenet-1k & EfficientNet  & 2.67 &  \textbf{1.23} & 2.56 & 2.50 \\
 imagenet-1k & PreResNet  & 6.59 &  15.44 & \textbf{3.59} & 3.71 \\
 imagenet-1k & ShuffleNet  & 35.38 &  89.58 & 19.54 & \textbf{18.48} \\
 imagenet-1k & VGG  & 0.84 &  \textbf{0.68} & 1.89 & 1.59 \\
 imagenet-1k & DLA  & 22.41 &  \textbf{8.49} & 14.69 & 15.68 \\
 imagenet-1k & HRNet  & 0.47 &  0.51 & \textbf{0.16} & 0.16 \\
 imagenet-1k & DRN-C  & 0.60 &  0.66 & \textbf{0.40} & 0.48 \\
 imagenet-1k & SqueezeNext  & 21.94 &  21.39 & 13.31 & \textbf{13.23} \\
 imagenet-1k & ESPNetv2  & 13.77 &  14.74 & \textbf{1.87} & 2.53 \\
 imagenet-1k & IGCV3  & 1.94 &  87.76 & 8.48 & \textbf{1.09} \\
 imagenet-1k & ProxylessNAS  & \textbf{0.19} &  0.26 & 0.28 & 0.26 \\
 imagenet-1k & SqueezeNet  & 0.11 &  0.11 & \textbf{0.07} & 0.08 \\
\hline
 cifar-10 & ResNet  & 0.31 &  0.30 & \textbf{0.28} & 0.28 \\
 cifar-10 & DIA-ResNet  & \textbf{0.05} &  0.08 & 0.28 & 0.32 \\
 cifar-10 & SENet  & 0.09 &  0.09 & \textbf{0.04} & 0.04 \\
\hline
 cifar-100 & ResNet  & 4.13 &  4.50 & \textbf{3.06} & 3.06 \\
 cifar-100 & DIA-ResNet  & \textbf{0.36} &  1.38 & 0.93 & 1.02 \\
 cifar-100 & SENet  & 0.36 &  0.43 & \textbf{0.26} & 0.26 \\
 cifar-100 & WRN  & 0.14 &  0.20 & 0.07 & \textbf{0.06} \\
\hline
 svhn & ResNet  & 0.04 &  0.04 & \textbf{0.02} & 0.02 \\
 svhn & DIA-ResNet  & 0.00 &  \textbf{0.00} & 0.02 & 0.02 \\
 svhn & SENet  & \textbf{0.00} &  0.00 & 0.00 & 0.00 \\
 svhn & WRN  & 0.01 &  0.01 & 0.01 & \textbf{0.01} \\
 svhn & ResNeXt  & 0.00 &  \textbf{0.00} & 0.01 & 0.01 \\
\hline
 cub-200-2011 & ResNet  & 0.20 &  \textbf{0.18} & 3.19 & 3.21 \\
 cub-200-2011 & SENet  & \textbf{1.07} &  1.29 & 1.85 & 1.95 \\
\hline
\end{tabular}
\end{center}
\caption{$MSE$ Results for all CV model regressions. }
\label{table:MSEresults}
\end{table}

\begin{table}[t]
\footnotesize  % \small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Dataset & Model  & $\log\Vert\cdot\Vert_{F}$ & $\log\Vert\cdot\Vert_{\infty}$ & $\hat{\alpha}$ & $\log\Vert\cdot\Vert^{\alpha}_{\alpha}$ \\
\hline
imagenet-1k & ResNet  & 0.82 &  0.67 & \textbf{0.90} & 0.88 \\
 imagenet-1k & EfficientNet  & 0.65 &  \textbf{0.84} & 0.67 & 0.67 \\
 imagenet-1k & PreResNet  & 0.73 &  0.36 & \textbf{0.85} & 0.85 \\
 imagenet-1k & ShuffleNet  & 0.63 &  0.06 & 0.80 & \textbf{0.81} \\
 imagenet-1k & VGG  & 0.71 &  \textbf{0.76} & 0.35 & 0.45 \\
 imagenet-1k & DLA  & 0.13 &  \textbf{0.67} & 0.43 & 0.39 \\
 imagenet-1k & HRNet  & 0.91 &  0.90 & \textbf{0.97} & 0.97 \\
 imagenet-1k & DRN-C  & 0.81 &  0.79 & \textbf{0.87} & 0.85 \\
 imagenet-1k & SqueezeNext  & 0.05 &  0.07 & 0.42 & \textbf{0.43} \\
 imagenet-1k & ESPNetv2  & 0.42 &  0.38 & \textbf{0.92} & 0.89 \\
 imagenet-1k & IGCV3  & 0.98 &  0.12 & 0.92 & \textbf{0.99} \\
 imagenet-1k & SqueezeNet  & 0.01 &  0.00 & \textbf{0.38} & 0.26 \\
 imagenet-1k & ProxylessNAS  & \textbf{0.68} &  0.56 & 0.53 & 0.58 \\
\hline
 cifar-10 & ResNet  & 0.58 &  0.59 & \textbf{0.62} & 0.61 \\
 cifar-10 & DIA-ResNet  & \textbf{0.96} &  0.93 & 0.74 & 0.71 \\
 cifar-10 & SENet  & 0.91 &  0.91 & \textbf{0.96} & 0.96 \\
\hline
 cifar-100 & ResNet  & 0.61 &  0.58 & \textbf{0.71} & 0.71 \\
 cifar-100 & DIA-ResNet  & \textbf{0.96} &  0.85 & 0.90 & 0.89 \\
 cifar-100 & SENet  & 0.97 &  0.96 & \textbf{0.98} & 0.98 \\
 cifar-100 & WRN  & 0.32 &  0.04 & 0.66 & \textbf{0.69} \\
\hline
 svhn & ResNet  & 0.69 &  0.70 & \textbf{0.82} & 0.81 \\
 svhn & DIA-ResNet  & 0.94 &  \textbf{0.95} & 0.78 & 0.77 \\
 svhn & SENet  & \textbf{0.99} &  0.96 & 0.98 & 0.98 \\
 svhn & WRN  & 0.13 &  0.10 & 0.20 & \textbf{0.21} \\
 svhn & ResNeXt  & 0.87 &  \textbf{0.90} & 0.64 & 0.75 \\
\hline
 cub-200-2011 & ResNet  & 0.94 &  \textbf{0.95} & 0.08 & 0.08 \\
 cub-200-2011 & SENet  & \textbf{0.66} &  0.59 & 0.41 & 0.38 \\
\hline
\end{tabular}
\end{center}
\caption{$R^{2}$ Results for all CV model regressions. }
\label{table:R2results}
\end{table}
